Notes and approaches to OCR

### 2020-11-29 outputs/documents/paper.Rmd
Update Google, Azure, and Pytesseract to the Sections approach.

Sometimes just by copying and pasting the information directly from the PDF is possible when it contains simple texts or regular tables. In that case, there is no barrier in the process of extracting data. But other times it is not as easy if it is an image, a survey form, or complex shapes containing relevant information, . Furthermore, there is a linguistic component that adds more complexity. For instance, it is well known that non-Latin characters such as Japanese, Chinese, Arabic, among others, generate several difficulties in different stages of the text mining process. It is because those characters have complicated structures, a huge number of categories, and resemblance among characters, font unevenness, or writing styles. In those cases, the need for reliable tools or methods with the ability to elicit data becomes extremely important.

@@

@@

| OCR Tool                             | Company	 | Type           |	Monthly Price Aug/2020 |	Tech Requierements |
| ------------------------------------ | --------- | -------------- | ------- | ------------------ |
| Azure Cognitive Services (OCR)       | Microsoft | API		        | Free Web Container: 5000/Free; <br/> <br/> S1 Web Container: 0-1M/$1.50 per 1,000 trans, 1M-5M/$1 per 1,000 trans, 5M-10M/$0.65 per 1,000 trans, 10M-100M/$0.65 per 1,000 trans, +100M/$0.65 per 1,000 trans        |                    |
| Amazon Rekognition	                 | Amazon	   | API		        | First 1 million images: $0.001 per image <br/> <br/> Next 9 million images $0.0008 per image <br/> <br/> Next 90 million images $0.0006 per image <br/> <br/> Over 100 million images $0.0004 per image         |                    |
| Tesseract		                         |           | R library      | Free	  |                    |
| PyTesseract (Wrapper Google's OCR Engine)    |           | Python Library | Free    |                    |
| OpenCV		                           |           | Python Library | Free	  |                    |
| Watson Visual Recognition	           | IBM	     | API		        | Lite: 1000/Free, <br/> <br/> Standard: $0.002 per trans      |                    |
| Kraken	(Linux OS)                   |           | Python Library	| Free	  |                    |
| Google Vision (for Text recognition) | Google	   | API		        | 1000/Free, 5 mill/$1.5, >5mill/$0.6        |                    |
| SwiftOCR	(iOS)                      | Apple	   | Swift Library  |         |                    | 		
| Amazon Textract	                     | Amazon	   | API		        | First 1 Million pages: $0.015 - $0.05 per page, <br/> <br/> Over 1 Million pages: $0.01 - $0.04 per page        |                    |
|	Tensorflow                           | Google    | Python Library | Free    |                    |

@@

Figure 1 presents a sample that corresponds to a Japanese text, but it also contains English text in some fragments of the text. The API offers the possibility to do self-detection, which in this case is helpful, but also the opportunity to specify the language in advance. Moreover, the orientation can also be self-detected or not.

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure1_full.png)
**Figure 1**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure2_full.png)
 **Figure 2**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure3_full.png)   
 **Figure 3**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure4_full.png)
 **Figure 4**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure5_full.png)
 **Figure 5**

@@

### Future Analysis

By doing some image preprocessing before the API call, it might be possible to see improvements in terms of boundary identification....

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure8.png)
 **Figure 8**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure9.png)
**Figure 9**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure10.png)
**Figure 10**

@@

Not clear at the moment.....I need to solve how to plot grouped characters vertically.

### Future Work

.........

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure12.png)
**Figure 12**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure13.png)
**Figure 13**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure14.png)
**Figure 14**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure15.png)   
 **Figure 15**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure16.png)   
 **Figure 16**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure17.png)   
 **Figure 17**

@@

.......

@@

.....................

### Future Work

@@

The training process itself is very friendly. However, the data preparation is the most important part as it generates the samples we feed into the model. Other studies pointed out that for languages such as Arabic, at least 800 lines are required to train a descent model. For the japanese text of this study we trained 36 lines in which several characters appear more than once.

>>>>

Sometimes just by copying and pasting the information directly from the PDF is possible when it contains simple texts or regular tables. In that case, there is no barrier in the process of extracting data. But other times it is not as easy if it is an image, a survey form, or complex shapes containing relevant information. Furthermore, there is a linguistic component that adds more complexity. For instance, it is well known that non-Latin characters such as Japanese, Chinese, Arabic, among others, generate several difficulties in different stages of the text mining process. It is because those characters have complicated structures, a huge number of categories, and resemblance among characters, font unevenness, or writing styles. In those cases, the need for reliable tools or methods with the ability to elicit data becomes extremely important.

@@

For the purpose of this study, one page from the letter a in the Japanese dictionary was taken to assess the tools. This image contains 3293 characters. Words in English were counted as one character for this analysis. MOreover, the sample text was divided into four images as it is illustrated in figure XX. These new images were assessed across all tools.

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/sections.png)
**Figure XX**

@@

| OCR Tool                             | Company	 | Type           |	Monthly Price Aug/2020 |	Tech Requierements |
| ------------------------------------ | --------- | -------------- | ------- | ------------------ |
| Azure Cognitive Services (OCR)       | Microsoft | API		        | Free Web Container: 5000/Free; <br/> <br/> S1 Web Container: 0-1M/$1.50 per 1,000 trans, 1M-5M/$1 per 1,000 trans, 5M-10M/$0.65 per 1,000 trans, 10M-100M/$0.65 per 1,000 trans, +100M/$0.65 per 1,000 trans        |                    |
| Amazon Rekognition	                 | Amazon	   | API		        | First 1 million images: $0.001 per image <br/> <br/> Next 9 million images $0.0008 per image <br/> <br/> Next 90 million images $0.0006 per image <br/> <br/> Over 100 million images $0.0004 per image         |                    |
| PyTesseract (Wrapper Google's OCR Engine)    |           | Python Library | Free    |                    |
Standard: $0.002 per trans      |                    |
| Kraken	(Linux OS)                   |           | Python Library	| Free	  |                    |
| Google Vision (for Text recognition) | Google	   | API		        | 1000/Free, 5 mill/$1.5, >5mill/$0.6        |                    |
| Amazon Textract	                     | Amazon	   | API		        | First 1 Million pages: $0.015 - $0.05 per page, <br/> <br/> Over 1 Million pages: $0.01 - $0.04 per page        |                    |
|	Kindai-OCR                           | Google    | Python Library | Free    |                    |

@@

Figure 1 presents a sample that corresponds to the section1 of the image containing Japanese text, but it also contains English text in some fragments of the text. The API offers the possibility to do self-detection, which in this case is helpful, but also the opportunity to specify the language in advance. Moreover, the orientation can also be self-detected or not.

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/section1.png)
**Figure 1**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/region-section1.png)
 **Figure 2**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/lines-section1.png)   
 **Figure 3**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/boundaries-section1.png)
 **Figure 4**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/characters-section1.png)
 **Figure 5**

@@

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/google-images/sections.png)
 **Figure 8**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/google-images/boundaries.png)
**Figure 9**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/google-images/characters.png)

**Figure 10**

@@

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/page.png)
**Figure 12**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/blocks.png)
**Figure 13**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/paragraphs.png)
**Figure 14**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/lines.png)   
 **Figure 15**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/boundaries.png)   
 **Figure 16**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/characters.png)   
 **Figure 17**

@@

The most important advantage is that this is a free library. It is also a wrapper from Google's Tesseract Engine. Moreover, the way it presents the covered areas are very detailed. It offers blocks, paragraphs, lines, boundaries, and finally the character level.

@@

@@

The training process itself is very friendly. However, the data preparation is the most important part as it generates the samples we feed into the model. Other studies pointed out that for languages such as Arabic, at least 800 lines are required to train a descent model. For the Japanese text of this study we trained 36 lines in which several characters appear more than once. The result after the training process was not good, indicating that the need of greater sample data might be needed which is not in the scope of this study.

# Other limitations

In order to use this library it is required to have either Linux or Mac. In this study, we use Google Colab which is offers a Linux environment to assess the library.
